Age-related changes in plant growth and traits

### 2016-05-25 nutrient.Rmd
add soils data

nutrient <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")

names(nutrient)
unique(nutrient$tissue_simple)

>>>>

nutrient <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")
soil <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_soil.csv")

plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)

names(soil)
names(nutrient)
unique(nutrient$tissue_simple)
